Regression Cube Analysis of Cohort Study Data

### 2015-03-21 draft.tex
revised abstract with Kais notes

%% Abstract section.
\abstract{%
%\com{Problem}.
Epidemiological studies comprise heterogeneous data about a subject group (a \emph{cohort}) to define disease-specific risk factors.
%%
These data contain information (\emph{features}) about a subjects' lifestyle, medical conditions and also medical image data.
%%
These features are analyzed using statistical regression analysis to identify feature combinations indicating a disease (the \emph{target feature}).
%%
Although there is a strong demand for overview visualizations of a whole data set towards a target feature, no suitable tool is available for epidemiological researchers.

%\com{New Solution}.
%%
We propose an analysis approach of epidemiological data sets by incorporating all features in an exhaustive regression-based analysis.
%%
This approach combines all \emph{independent features} with respect to a \emph{target feature} and provides a visualization, which reveals insight into the data by highlighting relationships.
%%
A 3D-visualization of all combinations of two to three independent features towards a target acts as an overview of the whole data set, the \emph{Regression Cube}.
%%
Slicing through the \emph{Regression Cube} allows for the detailed analysis of features towards the target disease.
%%
Expert knowledge about disease-specific hypotheses can be included into the analysis by adjusting the regression model formulas.
%%
Furthermore, the influences of features can be assessed using a difference view comparing different calculation results.
%%
%\com{Validation \& Results}.
%%
We applied our \emph{Regression Cube} method to a hepatic steatosis data set to reproduce results from a data-mining driven analysis.
%%
A qualitative analysis with three domain experts was conducted on a breast fat data set.
%%
We were able to derive new hypotheses about relations between breast fat density and breast lesions towards breast cancer.
%%
%\com{Implications}.
%%
With our work, we present a visual overview of epidemiological data with the \emph{Regression Cube}, which allows for the first time a interactive regression-based analysis of large feature sets with respect to a disease.
} % end of abstract

>>>>

%% Abstract section.
\abstract{%
%\com{Problem}.
Epidemiological studies comprise heterogeneous data about a subject group (a \emph{cohort}) to define disease-specific risk factors.
%%
These data contain information (\emph{features}) about a subjects' lifestyle, medical conditions and also medical image data.
%%
%These features are analyzed using statistical regression analysis to identify feature combinations indicating a disease (the \emph{target feature}).
%%
Statistical regression analysis is used to evaluate these features and to identify feature combinations indicating a disease (the \emph{target feature}).
%%
Although there is a strong demand for overview visualizations of a whole data set towards a target feature, no suitable tool is available for epidemiological researchers.

%\com{New Solution}.
%%
We propose an analysis approach of epidemiological data sets by incorporating all features in an exhaustive regression-based analysis.
%%
This approach combines all \emph{independent features} with respect to a \emph{target feature} and provides a visualization, which reveals insights into the data by highlighting relationships.
%%
A 3D-visualization of all combinations of two to three independent features towards a target acts as an overview of the whole data set, the \emph{Regression Cube}.
%%
Slicing through the \emph{Regression Cube} allows for the detailed analysis of features towards the target disease.
%%
Expert knowledge about disease-specific hypotheses can be included into the analysis by adjusting the regression model formulas.
%%
Furthermore, the influences of features can be assessed using a difference view comparing different calculation results.
%%
%\com{Validation \& Results}.
%%
We applied our \emph{Regression Cube} method to a hepatic steatosis data set to reproduce results from a data-mining driven analysis.
%%
A qualitative analysis with three domain experts was conducted on a breast fat data set.
%%
We were able to derive new hypotheses about relations between breast fat density and breast lesions towards breast cancer.
%%
%\com{Implications}.
%%
%With our work, we present a visual overview of epidemiological data with the \emph{Regression Cube}, which allows for the first time a interactive regression-based analysis of large feature sets with respect to a disease.
} % end of abstract
